%-------------------------
% Resume in Latex
% Author : Rasim Andiran
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{charter}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
	\textbf{\Huge \scshape Rasim Andiran} \\ \vspace{1pt}
	\small +90-507-547-4079 $|$ \href{mailto:resume@rasimandiran.com}{\underline{resume@rasimandiran.com}} $|$ 
	\href{https://linkedin.com/in/rasimandiran}{\underline{linkedin.com/in/rasimandiran}} $|$
	\href{https://github.com/rasimandiran}{\underline{github.com/rasimandiran}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
Results-driven Full-Stack Software Developer with extensive experience building scalable web and mobile applications. Successfully scaled a gaming platform to 100,000+ users with 50,000+ daily transactions using a microservices architecture. Skilled in backend development, API integration, and cloud infrastructure with AWS (Lambda, DynamoDB, S3), Python (Django, FastAPI), JavaScript (React, Next.js, Express.js), and databases like PostgreSQL and MySQL. Key achievements include developing a \$100M+ asset management platform, integrating 20+ cryptocurrency exchanges, and managing 50+ API integrations for real-time data synchronization. Known for hands-on coding, and delivering impactful solutions in fast-paced environments. Ready to drive innovation and system efficiency in challenging projects.

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
  {Fullstack Software Developer}{November 2023 -- Present}
  {Online Gaming Platform}{Remote}
  \resumeItemListStart
    \resumeItem{System Overhaul \& Scalability: Rebuilt the entire legacy codebase from scratch, transitioning to a service-oriented architecture (SOA) with 15+ microservices, supporting 100,000+ users and processing 50,000+ games daily.}
    \resumeItem{Backend \& Database Development: Redesigned PostgreSQL database for scalability, improved performance using Redis and Kafka, and integrated real-time processing features like live chat and user progression tracking.}
    \resumeItem{Full-Stack Collaboration: Led backend development while contributing to frontend features using Next.js, enhancing user experience and supporting complex game logic.}
  \resumeItemListEnd
        
  \resumeSubheading
  {Chief Technology Officer}{February 2021 -- June 2023}
  {Idealex}{Baku, Azerbaijan}
  \resumeItemListStart
    \resumeItem{Technical Leadership \& System Architecture: Designed and implemented the entire technical infrastructure for both B2C (crypto and stock trading platform) and B2B (API product for financial institutions) services, integrating over 20 exchanges to provide optimal pricing and additional features like staking.}
    \resumeItem{Cloud Infrastructure \& DevOps: Built a scalable, serverless architecture using AWS services (DynamoDB, Lambda, S3, CloudFront, Amplify and more), ensuring system reliability, security, and high availability.}
    \resumeItem{Team Leadership: Led a cross-functional team of 10, including 4 backend developers, 2 mobile developers, 2 designers, and 2 frontend developers, while contributing directly to the codebase and driving best coding practices.}
    \resumeItem{ Strategic \& Client-Facing Role: Managed partnerships with third-party providers, negotiated service agreements, led technical discussions with B2B clients, and played a key role in strategic decision-making alongside the executive team.}
  \resumeItemListEnd

  \resumeSubheading
  {Fullstack Software Developer}{February 2020 -- February 2021}
  {BV Crypto}{Remote}
  \resumeItemListStart
    \resumeItem{System Design \& Development: Designed and implemented a comprehensive fund management system for a hedge fund managing over \$100M in assets, enabling real-time tracking, investment management, and fund performance reporting through a scalable backend architecture.}
    \resumeItem{Data Integration \& Automation: Integrated 50+ APIs for real-time price updates of various investment instruments, ensuring instant sync. and up-to-date performance metrics like AUM, Sharpe Ratio, and other critical KPIs.}
    \resumeItem{Financial Data Visualization: Built custom dashboards for fund managers with live financial analytics, ensuring personalized access levels and secure data visibility based on user permissions.}
  \resumeItemListEnd

  \resumeSubheading
  {Fullstack Software Developer}{February 2018 -- January 2020}
  {Talenta Solutions}{Bursa, Turkey}
  \resumeItemListStart
    \resumeItem{P2P Cryptocurrency Exchange Development: Designed and implemented P2P/non-P2P crypto exchanges, including frontend and backend components using PHP and Express.js, with high-performance order-matching engines developed in C/C++}
    \resumeItem{Market-Making Bot Integration: Built and deployed a market-making bot integrated with 8-10 exchanges, enhancing trading operations and liquidity through automated trading algorithms.}
    \resumeItem{Gig Economy Platform Development: Enhanced mobile user experience by building a Progressive Web App, while developing scalable backend services and managing AWS cloud infrastructure for secure and resilient deployment.}
  \resumeItemListEnd

  \resumeSubheading
  {Fullstack Software Developer}{August 2016 -- February 2018}
  {Behrud Technology}{Bursa, Turkey}
  \resumeItemListStart
    \resumeItem{Travel \& Ticketing Systems: Developed a flight ticketing system using Amadeus GDS API with Django and Tornado frameworks, supporting high-volume ticket sales and generating custom travel reports for trend analysis and business insights.}
    \resumeItem{Insurance \& 3D Modeling Platform: Built the backend and back-office portal for a car damage detection app, managing complex 3D modeling processes for insurance claims automation.}
    \resumeItem{Telecom \& Integration Solutions: Developed the backend for a virtual SIM card app, integrating voice-over-web services and third-party APIs, enhancing telecom service scalability.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
		\textbf{Languages}{: Python, JavaScript, TypeScript, PHP,  C/C++, SQL, HTML/CSS } \\
		\textbf{Frameworks}{: Django, Flask, FastAPI, Tornado, React, Next.js, Express.js, Nest, Codeigniter, Laravel } \\
		\textbf{Databases}{: MySQL, PostgreSQL, DynamoDB, MongoDB, Redis } \\
		\textbf{Cloud}{: AWS, GCP, Firebase } \\
		\textbf{Tools}{: Git, Docker, Jenkins, Github Actions, Jira} \\
		\textbf{Libraries}{: Pandas, NumPy, Matplotlib, scikit-learn}
	}}
\end{itemize}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
  {Uludag University}{Bursa, Turkey}
  {Bachelor of Science (B.Sc.) in Electrical and Electronics Engineering}{}
  \resumeSubheading
  {Istanbul University}{Istanbul, Turkey}
  {Bachelor of Science (B.Sc.) in Management Information Systems}{}
  \resumeSubheading
  {Anadolu University}{Eskisehir, Turkey}
  {Associate Degree in Web Design and Development}{}
\resumeSubHeadingListEnd

\end{document}